---
title: "ImgHelpR-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ImgHelpR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ImgHelpR)
library (jpeg)
```

This document introduces you to ImgHelpR's functions and how to use them.

ImgHelpR makes basic image manipulation easy in R. With ImgHelpR, beginners can easily crop, rotate, compress, or change the color scale of a given image

## Data

To explore basic image manipulation with ImgHelpR, a test image named `ubc.jpeg` has been provided. The JPEG image needs to be read in as an array; we recommend using via `jpeg::readJPEG('path')` . To display the image,

```{r}
# read image in via JPEG
ubc <- jpeg::readJPEG('../test_img/ubc.jpeg')

# display test image 
plot(0:1,0:1,type='n',ann=FALSE,axes=FALSE)
rasterImage(ubc, 0,0,1,1)
```

## Functions

ImgHelpR is comprised of 4 main functions:

-   `Crop(img, width, height)` This function takes an image and the desired height/width as input, and returns a cropped image.

-   `ImgRotate(img, degree)` This function rotates an image either 90, 180, 270, or 360 degrees from it's original orientation.

-   `ColorConv(img, color)` This function converts an image to a color specified by user-input.

-   `ImgCompress(img, method, level=1)` This function compresses an image to a user-defined compression level.

## Crop Images with Crop()

-   `Crop()` cuts an image's dimensions to a desired size. There are three inputs, `img`, `height`, `width` that must be inputted by the user. The function returns an array, which can be read into `rasterImage` as shown in the **Data** section.

```{r}
# display test image 
plot(0:1,0:1,type='n',ann=FALSE,axes=FALSE)
rasterImage(ubc, 0,0,1,1)

# crop image
cropped_ubc <- Crop(ubc, 250, 250)

org_dim <- dim(ubc)
crop_dim <- dim(cropped_ubc)

# display cropped image
plot(0:1,0:1,type='n',ann=FALSE,axes=FALSE)
rasterImage(cropped_ubc, 0,0,1,1)

# print current dimensions of test image
print('Original dimensions: ') 
org_dim
print("Cropped dimensions: ")
crop_dim
```

## Rotate Images with ImgRotate()

`ImgRotate()` rotates an image 90, 180, 270, or 360 degrees counterclockwise. There are two inputs, `img` and `degree`, that must be inputted by the user. The function returns an array, which can be read into `rasterImage` as shown in the **Data** section.

```{r}
# display test image 
plot(0:1,0:1,type='n',ann=FALSE,axes=FALSE)
rasterImage(ubc, 0,0,1,1)

# rotate image 
ubc_180 <- ImgRotate(ubc, 180)

# display rotated image
plot(0:1,0:1,type='n',ann=FALSE,axes=FALSE)
rasterImage(ubc_180, 0,0,1,1)
```

## Convert Images color with ColorConv()

```{r}
# display test image 
plot(0:1,0:1,type='n',ann=FALSE,axes=FALSE)
rasterImage(ubc, 0,0,1,1)

# convert to gray 

```

## Compress Images with ImgCompress()

```{r}
# display test image 
plot(0:1,0:1,type='n',ann=FALSE,axes=FALSE)
rasterImage(ubc, 0,0,1,1)
```
